Finding Maximum $k$-Cliques Faster \\ Using Lazy Global Domination

### 2016-07-01 talk/talk.tex
Punctuation

\begin{frame}{Existing Work}
    \begin{itemize}
        \item Many computational papers on the $k$-club problem
            \begin{itemize}
                \item Not a hereditary property, and modelling it is hard, so lots of scope for
                    being clever.
            \end{itemize}

@@

\begin{frame}{The Results}
    \begin{itemize}
        \item Erd\H{o}s collaboration graphs (up to 6,927 vertices, 11,850 edges)
            \begin{itemize}
                \item 16 take $<1s$, 2 take $<12s$, 3 $>1h$.
            \end{itemize}

        \item DIMACS 2 Clique Graphs (up to 500 vertices, 46,627 edges)
            \begin{itemize}
                \item 22 take $<1s$, 2 take $>1h$.
            \end{itemize}

        \item DIMACS 10 Partitioning Graphs (smallest 20, up to 36,519 vertices, 1,007,284 edges)
            \begin{itemize}
                \item 2 take $>1h$, most take well under a minute.
            \end{itemize}

        \item DIMACS 10 Clustering Graphs (smallest 20, up to 40,421 vertices, 175,691 edges)
            \begin{itemize}
                \item 7 take $>1h$, most take well under a minute.
            \end{itemize}
    \end{itemize}
\end{frame}

@@

\begin{frame}{Better Results!}
    \begin{itemize}
        \item Erd\H{o}s collaboration graphs
            \begin{itemize}
                \item The three open instances now take 3.8s, 69.4s, 207.3s.
            \end{itemize}

        \item DIMACS 2 Clique Graphs
            \begin{itemize}
                \item The two open instances now take 0.1s.
            \end{itemize}

        \item DIMACS 10 Partitioning Graphs
            \begin{itemize}
                \item One open instance now takes 16.9s, the other still takes $>1h$.
            \end{itemize}

        \item DIMACS 10 Clustering Graphs
            \begin{itemize}
                \item Two open instances closed.
            \end{itemize}

        \item Not a universal success, though
            \begin{itemize}
                \item Factor of 10 slowdown on a few fairly easy instances.
                \item Without laziness, the results are terrible\ldots
            \end{itemize}
    \end{itemize}
\end{frame}

>>>>

\begin{frame}{Existing Work}
    \begin{itemize}
        \item Many computational papers on the $k$-club problem.
            \begin{itemize}
                \item Not a hereditary property, and modelling it is hard, so lots of scope for
                    being clever.
            \end{itemize}

@@

\begin{frame}{The Results}
    \begin{itemize}
        \item Erd\H{o}s collaboration graphs (up to 6,927 vertices, 11,850 edges):
            \begin{itemize}
                \item 16 take $<1s$, 2 take $<12s$, 3 $>1h$.
            \end{itemize}

        \item DIMACS 2 Clique Graphs (up to 500 vertices, 46,627 edges):
            \begin{itemize}
                \item 22 take $<1s$, 2 take $>1h$.
            \end{itemize}

        \item DIMACS 10 Partitioning Graphs (smallest 20, up to 36,519 vertices, 1,007,284 edges):
            \begin{itemize}
                \item 2 take $>1h$, most take well under a minute.
            \end{itemize}

        \item DIMACS 10 Clustering Graphs (smallest 20, up to 40,421 vertices, 175,691 edges):
            \begin{itemize}
                \item 7 take $>1h$, most take well under a minute.
            \end{itemize}
    \end{itemize}
\end{frame}

@@

\begin{frame}{Better Results!}
    \begin{itemize}
        \item Erd\H{o}s collaboration graphs:
            \begin{itemize}
                \item The three open instances now take 3.8s, 69.4s, 207.3s.
            \end{itemize}

        \item DIMACS 2 Clique Graphs:
            \begin{itemize}
                \item The two open instances now take 0.1s.
            \end{itemize}

        \item DIMACS 10 Partitioning Graphs:
            \begin{itemize}
                \item One open instance now takes 16.9s, the other still takes $>1h$.
            \end{itemize}

        \item DIMACS 10 Clustering Graphs:
            \begin{itemize}
                \item Two open instances closed.
            \end{itemize}

        \item Not a universal success, though:
            \begin{itemize}
                \item Factor of 10 slowdown on a few fairly easy instances.
                \item Without laziness, the results are terrible\ldots
            \end{itemize}
    \end{itemize}
\end{frame}
